Reanalysis Step 5: Outcome Analysis with Three-Way Interaction

### 2025-09-04 reanalysis-5-outcome_analysis-interaction.qmd
shared test

if (file.exists(models_cache_file) && !force_refit_models) {
  # Load cached models
  cached_models <- readRDS(models_cache_file)
  models <- cached_models$models
  model_summaries <- cached_models$model_summaries
  model_progress <- cached_models$model_progress
  models_loaded_from_cache <- TRUE
  cache_location <- models_cache_file
  log_message("Models loaded from cache: ", cache_location)
} else {
  # Fit new models
  models_loaded_from_cache <- FALSE
  models <- list()
  model_summaries <- list()

@@

  # Save to cache
  cached_models <- list(
    models = models,
    model_summaries = model_summaries,
    model_progress = model_progress,
    formula_used = interaction_formula,
    n_imputations = n_imputations,
    timestamp = Sys.time()
  )

  saveRDS(cached_models, models_cache_file)
  cache_location <- models_cache_file
  log_message("Models fitted and saved to cache: ", cache_location)
}

>>>>

if (file.exists(models_cache_file) && !force_refit_models) {
  # Load cached models (just the models list, not a complex structure)
  models <- readRDS(models_cache_file)
  models_loaded_from_cache <- TRUE
  cache_location <- models_cache_file
  log_message("Models loaded from cache: ", cache_location)

  # Rebuild model_progress from loaded models
  model_progress <- data.frame(
    Imputation = integer(),
    Converged = logical(),
    ThreeWay_Terms = integer()
  )

  for (i in 1:length(models)) {
    coef_summary <- summary(models[[i]])$coefficients
    threeway_terms <- grep("ever_lapse_binary.*:dr_severity.*:any_treatment", 
                           rownames(coef_summary), value = TRUE)
    model_progress <- rbind(model_progress, data.frame(
      Imputation = i,
      Converged = models[[i]]$converged,
      ThreeWay_Terms = length(threeway_terms)
    ))
  }
} else {
  # Fit new models
  models_loaded_from_cache <- FALSE
  models <- list()
  model_summaries <- list()

@@

  # Save to cache - models only, not the full cached_models list to save memory
  saveRDS(models, models_cache_file)
  cache_location <- models_cache_file
  log_message("Models fitted and saved to cache: ", cache_location)
}
